Wrinkling and yielding of protein gels

### 2013-09-10 poster_Rome.tex
forgotten file
logos full ref of Gallot et al.

\LHead{\textsc{Laboratoire de Physique -- UMR 5672, Ecole Normale Supérieure de Lyon}}

@@

\begin{textblock}{3}(0,10)
	Corresponds with the fall of $G^\prime$.

	\Subhead{Length scales}
	\begin{itemize}
	\item A fundamental that does not evolve
	\item Nested structures as ``harmonics''
	\end{itemize}
	\Subhead{Qualitatively different from}
	\begin{itemize}
	\item phase separation patterns 
	\item Turing patterns
	\item usual wrinkles
	\end{itemize}	 
\end{textblock}

@@

	\begin{tikzpicture}[inner sep=0]
		\node[above right]{\includegraphics[width=\textwidth]{collage_cut}};
		\draw[ultra thick] ++(0,0.5em) -- ++(0.33\textwidth,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}\\
	Tiled, enhanced relief
\end{textblock}

@@

	\begin{tikzpicture}[ultra thick, font=\small]
	\node[above right, inner sep=0] (sch) {\includegraphics[width=0.4\textwidth]{usv_3D_image}};
	\draw[<-] (0.3\textwidth,0.11\textwidth) -- +(1em,0) node[right] {water in};
	\draw[->] (0.3\textwidth,0.07\textwidth) -- +(1em,0) node[right] {water out};
	\node[right] at (0.2\textwidth, 0.3\textwidth) (rh) {rheometer};
	\node[above right] at (0.2\textwidth, 0) (arraylabel) {array of transducers};
	\draw[->,dotted]	 (arraylabel.west) -- (0.1\textwidth, 0.1\textwidth);
	\draw[->] (0.06\textwidth, 0.15\textwidth) -- (0,0.15\textwidth) node[draw, left, text width=0.18\textwidth] (mce) {multi-channel electronics};
	\node[above=of mce, draw] (pc) {PC};
	\draw[->] (mce)-- (pc);
	\draw[->] (rh) -- +(0,1em) -| (pc.north);
	\node[below right=1em and 0 of mce.south west, text width=0.18\textwidth] {Gallot et al. RSI (2013).};
	\node[below right =of sch.north east, text width=0.32\textwidth] {3\% of \SI{30}{\micro\metre} acrylamide beads as contrast agent};
	\end{tikzpicture}

>>>>

\LHead{\raisebox{-0.3em}{\includegraphics[height=\baselineskip]{CNRSfilaire-Q}\qquad\includegraphics[height=\baselineskip]{logo_UCBL}\qquad}\textsc{Laboratoire de Physique, Ecole Normale Supérieure de Lyon}\raisebox{-0.3em}{\qquad\includegraphics[height=\baselineskip]{logo_ens-lyon}}}

@@

\begin{textblock}{3}(0,10)
	\Subhead{Length scales}
	\begin{itemize}
	\item A fundamental that does not evolve
	\item Nested structures as ``harmonics''
	\end{itemize}
	\Subhead{Qualitatively different from}
	\begin{itemize}
	\item Phase separation patterns 
	\item Turing patterns
	\item Usual wrinkles
	\end{itemize}	 
\end{textblock}

@@

	\begin{tikzpicture}[inner sep=0]
		\node[above right]{\includegraphics[width=\textwidth]{collage_cut}};
		\draw[ultra thick] ++(0,0.5em) -- ++(0.33\textwidth,0) node[pos=0.5, below=0.25em, font=\small] {\SI{1}{\milli\metre}};
	\end{tikzpicture}\\
	Tiled, enhanced elevation
\end{textblock}

@@

	\begin{tikzpicture}[ultra thick, font=\small]
	\node[above right, inner sep=0] (sch) {\includegraphics[width=0.4\textwidth]{usv_3D_image}};
	\draw[<-] (0.3\textwidth,0.11\textwidth) -- +(1em,0) node[right] {water in};
	\draw[->] (0.3\textwidth,0.07\textwidth) -- +(1em,0) node[right] {water out};
	\node[right] at (0.2\textwidth, 0.3\textwidth) (rh) {rheometer};
	\node[above right] at (0.2\textwidth, 0) (arraylabel) {array of transducers};
	\draw[->,dotted]	 (arraylabel.west) -- (0.1\textwidth, 0.1\textwidth);
	\draw[->] (0.06\textwidth, 0.15\textwidth) -- (0,0.15\textwidth) node[draw, left, text width=0.18\textwidth] (mce) {multi-channel electronics};
	\node[above=of mce, draw] (pc) {PC};
	\draw[->] (mce)-- (pc);
	\draw[->] (rh) -- +(0,1em) -| (pc.north);
	\node[above right=0 and 0.1\textwidth of sch.south east, text width=0.25\textwidth, align=right] {Gallot et al. \linebreak\textit{Rev. Sci. Instrum.} 84, 045107 (2013).};
	\node[below right =of sch.north east, text width=0.32\textwidth] {3\% of \SI{30}{\micro\metre} acrylamide beads as contrast agent};
	\end{tikzpicture}
